\chapter*{Curriculum vitae}
\addcontentsline{toc}{chapter}{Curriculum vitae}
\pagestyle{plain}
\fancyfoot[RE, LO]{\thepage}
%\markboth{CURRICULUM VITAE}{ }
%\renewcommand{\sectionmark}[1]{ \markright{ \MakeUppercase{#1} } }

% =============== Start of CV ====================
% Adapted from: Copyright (C) 2022 CDN (Diego) Damasceno

% Sections formatting
\titleformat{\section}{\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule]
\titleformat{\subsection}{\bfseries\raggedright\large}{}{0em}{}[]

% Phone and Email as hyperlinks

% CV Info (to be customized).
\newcommand{\CVAuthor}{Lukas Valentin Graf, MSc Paris-Lodron University, Salzburg, in Applied Geoinformatics}
%\newcommand{\CVTitle}{My short name's CV}


\begin{cv}{}
\section{Personal Information}
  \begin{cvlist}{}
    \item Lukas Valentin Graf, MSc Paris-Lodron University Salzburg, in Applied Geoinformatics
    \item 
        Date of birth: 29 April 1996\\
        Nationality: German
  \end{cvlist}
  
% \vspace{-0.75cm}
 \section{Education}
  \begin{cvlist}{}
  \item[May 21--Feb 24] 
      \textbf{Doctorate,} {ETH Zürich}\\ 
      %ETH Zürich, Switzerland\\
      \textbf{Thesis:} {Prototyping of a landscape-scale phenotyping approach for quantification of winter wheat growth and development}
  \item[Oct 18--Aug 20] 
      \textbf{Msc,} {{\textbf{Applied Geoinformatics, }}}{Paris-Lodron University Salzburg, Austria}\\
      \textbf{Thesis:} {Semantic Segmentation and Multi-Temporal Analysis of Sentinel-2 Imagery for Mapping Centre Pivot Irrigation Systems}
  \item[Oct 14--Jan 18] 
      \textbf{BSc,} {{\textbf{Geography (major) and meteorology (minor), }} }{Ludwig-Maximilians-University München, Germany}\\ 
      \textbf{Thesis:} {Derivation of plant-physiological parameters from multi- and hyperspectral remote sensing data using a radiative transfer model}
  \end{cvlist}


\subsection{Supervision and advisory of BSc and MSc students}
\begin{cvlist}{}
    \item[Oct 23--Feb 24]
    {\textit{Vilma Rantanen}, }
    BSc Thesis: Zusammenhang zwischen grünem Blattflächenindex, Biomasse und Bodenbedeckungsgrad in Winterweizen (Relationship between green leaf area index, biomass and soil cover in winter wheat)
    \item[Mar 23--Sept 23]
    {\textit{Julian Neff}, }
    MSc Thesis: Guided Super-Resolution for Retrieval of Crop Functional Traits from Sentinel-2 Imagery
    \item[Mar 22--Sept 22]
    {\textit{Samuel Wildhaber}, }
    MSc Thesis: Comparison and Validation of Planet Scope and Sentinel-2 Satellite Data for Wheat Leaf Area Estimation in Eschikon
\end{cvlist}
  
\section{Work Experience}
  \begin{cvlist}{}
    \item[Jan 17--Apr 21]
      {\textbf{Software developer, }}{\textit{Vista Remote Sensing in Geosciences GmbH}, München, Germany}
    \item[Jan 17--Feb 18]
      {\textbf{Scientific assistant, }}{\textit{Department of Geography, Ludwig-Maximilians-University}, München, Germany}
    \item[Jul 17--Oct 17]
      {\textbf{Research internship, }}{\textit{University of the Balearic Islands}, Palma de Mallorca, Spain}
    \item[Oct 16--Dec 16]
     {\textbf{Research internship, } }{\textit{German Aerospace Center}, Oberpfaffenhofen, Germany}
  \end{cvlist}


\section{Publications}
\subsection{First author publications}
\begin{cvlist}{}

    \item[2023]
    Graf, L. V., Merz, Q. N., Walter, A., \& Aasen, H. (2023). Insights from Field Phenotyping Improve Satellite Remote Sensing Based In-Season Estimation of Winter Wheat Growth and Phenology. Remote Sensing of Environment, 299, 113860. \url{https://doi.org/10.1016/j.rse.2023.113860}

    \item[2023]
    Graf, L.V., Gorroño, J., Hueni, A., Walter, A., \& Aasen, H. (2023). Propagating Sentinel-2 Top-of-Atmosphere Radiometric Uncertainty into Land Surface Phenology Metrics Using a Monte Carlo Framework. IEEE Journal of Selected Topics in Applied Earth Observations and Remote Sensing, 16, 8632-8654. \url{https://doi.org/10.1109/JSTARS.2023.3297713}

    \item[2022]
    Graf, L. V., Perich, G., \& Aasen, H. (2022). EOdal: An open-source Python package for large-scale agroecological research using Earth Observation and gridded environmental data. Computers and Electronics in Agriculture, 203, 107487. \url{https://doi.org/10.1016/j.compag.2022.107487}

\end{cvlist}

\subsection{Co-author publications}

\begin{cvlist}

    \item[2023]
    Kooistra, L., Berger, K., Brede, B., \textbf{Graf, L.V.}, Aasen, H., Roujean, J.-L., Machwitz, M., Schlerf, M., Atzberger, C., Prikaziuk, E., Ganeva, D., Tomelleri, E., Croft, H., Reyes Muñoz, P., Garcia Millan, V., Darvishzadeh, R., Koren, G., Herrmann, I., Rozenstein, O., Belda, S., Rautiainen, M., Rune Karlsen, S., Figueira Silva, C., Cerasoli, S., Pierre, J., Tanır Kayıkçı, E., Halabuk, A., Tunc Gormus, E., Fluit, F., Cai, Z., Kycko, M., Udelhoven, T., \& Verrelst, J. (2023). Reviews and syntheses: Remotely sensed optical time series for monitoring vegetation productivity. Biogeosciences, 1–67. \url{https://doi.org/10.5194/bg-2023-88}

    \item[2023]
    Perich, G., Turkoglu, M. O., \textbf{Graf, L. V.}, Wegner, J. D., Aasen, H., Walter, A., \& Liebisch, F. (2023). Pixel-based yield mapping and prediction from Sentinel-2 using spectral indices and neural networks. Field Crops Research, 292, 108824. \url{https://doi.org/10.1016/j.fcr.2023.108824}

 
\end{cvlist}

\end{cv}
